A Methodology and Implementation of Automated Emissions Harmonization for Use in Integrated Assessment Models

### 2018-02-08 paper.tex
update data.ene to software.ene

\texttt{aneris}, first made available in 2017, is available online at
\url{https://github.com/iiasa/aneris} as a free and open-source Python software
library (approximately 2000 lines of code). The \texttt{aneris} software was
developed by the lead author whose contact information is shown on the title
page of this manuscript. Documentation for the \texttt{aneris} Python package,
including software requirements, is available online at
\url{http://data.ene.iiasa.ac.at/gidden/aneris/}.

@@

The remainder of this paper describes the methodology and implementation of the
harmonization software \code{aneris} \cite{matthew_gidden_2017_802832}, written
in the Python programming language (detailed documentation is available online
at \url{http://data.ene.iiasa.ac.at/gidden/aneris/}). Section \ref{sec:meths}
provides a detailed description of the underlying mathematical components of
\code{aneris} as well as the procedural workflow. A case study of applying the
automated harmonization mechanism on two example \gls{iam} scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.

@@

\begin{listing}[H]
\begin{minted}{python}
from aneris.tutorial import load_data
model, hist, driver = load_data()
for scenario in driver.scenarios():
    driver.harmonize(scenario)
harmonized, metadata = driver.harmonized_results()
\end{minted}
\caption{High-level user interaction with the \texttt{HarmonizationDriver} taken from the online \href{http://data.ene.iiasa.ac.at/gidden/aneris/tutorial.html}{tutorial}}
\label{lst:tutorial}
\end{listing}

@@

optional arguments:
  -h, --help            show this help message and exit
  --history HISTORY     Historical emissions in the base year.
  --regions REGIONS     Mapping of country iso-codes to native regions.
  --rc RC               Runcontrol YAML file (see
                        http://data.ene.iiasa.ac.at/gidden/aneris/config.html for
                        examples).
  --output_path OUTPUT_PATH
                        Path to use for output file names.
  --output_prefix OUTPUT_PREFIX
                        Prefix to use for output file names.
\end{minted}
\caption{The \gls{cli} help provided by the \code{aneris} package.}
\label{lst:cli}
\end{listing}

@@

Users are able to control the harmonization process via a number of options
(with examples provided
\href{http://data.ene.iiasa.ac.at/gidden/aneris/config.html}{online}). The primary mechanism
by which users control the process is by providing \textit{override} methods for
any combination of region and variable (i.e., sector and gas species).  In
practice, it may be possible that not all default methods chosen will provide
robust harmonized trajectories, especially if there is a significant difference
between historical and model values in the harmonization year, if there is
significant upward or downward movement in the model trajectory, or if there are
known discrepancies in sectoral definition between the \gls{iam} and historical data
source. In such cases, users can override default methods with their method of
choice and both the default method and override is reported in the resulting
metadata.

>>>>

\texttt{aneris}, first made available in 2017, is available online at
\url{https://github.com/iiasa/aneris} as a free and open-source Python software
library (approximately 2000 lines of code). The \texttt{aneris} software was
developed by the lead author whose contact information is shown on the title
page of this manuscript. Documentation for the \texttt{aneris} Python package,
including software requirements, is available online at
\url{http://software.ene.iiasa.ac.at/aneris/}.

@@

The remainder of this paper describes the methodology and implementation of the
harmonization software \code{aneris} \cite{matthew_gidden_2017_802832}, written
in the Python programming language (detailed documentation is available online
at \url{http://software.ene.iiasa.ac.at/aneris/}). Section \ref{sec:meths}
provides a detailed description of the underlying mathematical components of
\code{aneris} as well as the procedural workflow. A case study of applying the
automated harmonization mechanism on two example \gls{iam} scenarios, one with
emissions growth and another with emissions mitigation, is presented in Section
\ref{sec:results}. Finally, the general effectiveness and potential future
improvements on the automated methodology is discussed in Section
\ref{sec:future}.

@@

\begin{listing}[H]
\begin{minted}{python}
from aneris.tutorial import load_data
model, hist, driver = load_data()
for scenario in driver.scenarios():
    driver.harmonize(scenario)
harmonized, metadata = driver.harmonized_results()
\end{minted}
\caption{High-level user interaction with the \texttt{HarmonizationDriver} taken from the online \href{http://software.ene.iiasa.ac.at/aneris/tutorial.html}{tutorial}}
\label{lst:tutorial}
\end{listing}

@@

optional arguments:
  -h, --help            show this help message and exit
  --history HISTORY     Historical emissions in the base year.
  --regions REGIONS     Mapping of country iso-codes to native regions.
  --rc RC               Runcontrol YAML file (see
                        http://software.ene.iiasa.ac.at/aneris/config.html for
                        examples).
  --output_path OUTPUT_PATH
                        Path to use for output file names.
  --output_prefix OUTPUT_PREFIX
                        Prefix to use for output file names.
\end{minted}
\caption{The \gls{cli} help provided by the \code{aneris} package.}
\label{lst:cli}
\end{listing}

@@

Users are able to control the harmonization process via a number of options
(with examples provided
\href{http://software.ene.iiasa.ac.at/aneris/config.html}{online}). The primary mechanism
by which users control the process is by providing \textit{override} methods for
any combination of region and variable (i.e., sector and gas species).  In
practice, it may be possible that not all default methods chosen will provide
robust harmonized trajectories, especially if there is a significant difference
between historical and model values in the harmonization year, if there is
significant upward or downward movement in the model trajectory, or if there are
known discrepancies in sectoral definition between the \gls{iam} and historical data
source. In such cases, users can override default methods with their method of
choice and both the default method and override is reported in the resulting
metadata.
